A Fast Unified Model for Parsing and Sentence Understanding

### 2016-05-31 writing/hard_stack_paper/paper.tex
meta-meta-edit: Use a clearer sexpr notation in thin-stack example

\begin{table}[t]
\centering
\begin{tabular}{cc @{\hspace*{2em}}c @{\hspace*{2em}} l}
  \toprule
  $t$ & $a_t$ & $S$[$t$] & \multicolumn{1}{c}{$Q_t$} \\
  \midrule
  0 & \shift &  & \underline{\hphantom{0} \hphantom{0}} \\
  1 & \shift & \word{Spot} & \hphantom{0} \underline{\hphantom{0} 1} \\
  2 & \shift & \word{sat} & \hphantom{0} \hphantom{0} \underline{1 2} \\
  3 & \reduce & \word{down} & \hphantom{0} \hphantom{0} 1 \underline{2 3} \\
  4 & \reduce & \word{sat down} & \hphantom{0} \hphantom{0} \underline{1 4} \\
  5 & & \word{Spot} (\word{sat down}) & \hphantom{0} \underline{\hphantom{0} 5} \\
  \bottomrule
\end{tabular}
\caption{The thin-stack algorithm operating on the input sequence $\mathbf x = \text{(\word{Spot}, \word{sat}, \word{down})}$ and the transition sequence shown in the second column. $S$ is shown in the third column and represents the top of the stack at each step $t$. The last two elements of $Q$ (underlined) specify which rows $t$ would be involved in a \reduce\ operation at the next step.}
\label{tbl:thin-stack}
\end{table}

>>>>

\begin{table}[t]
\centering
\begin{tabular}{cc @{\hspace*{2em}}c @{\hspace*{2em}} l}
  \toprule
  $t$ & $a_t$ & $S$[$t$] & \multicolumn{1}{c}{$Q_t$} \\
  \midrule
  0 & \shift &  & \underline{\hphantom{0} \hphantom{0}} \\
  1 & \shift & \word{Spot} & \hphantom{0} \underline{\hphantom{0} 1} \\
  2 & \shift & \word{sat} & \hphantom{0} \hphantom{0} \underline{1 2} \\
  3 & \reduce & \word{down} & \hphantom{0} \hphantom{0} 1 \underline{2 3} \\
  4 & \reduce & (\word{sat down}) & \hphantom{0} \hphantom{0} \underline{1 4} \\
  5 & & (\word{Spot} (\word{sat down})) & \hphantom{0} \underline{\hphantom{0} 5} \\
  \bottomrule
\end{tabular}
\caption{The thin-stack algorithm operating on the input sequence $\mathbf x = \text{(\word{Spot}, \word{sat}, \word{down})}$ and the transition sequence shown in the second column. $S$ is shown in the third column and represents the top of the stack at each step $t$. The last two elements of $Q$ (underlined) specify which rows $t$ would be involved in a \reduce\ operation at the next step.}
\label{tbl:thin-stack}
\end{table}
